Accurate evaluation of dislocation tractions

### 2021-01-13 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Finished editing pictures. Sync to overleaf next.

It is also worth looking at the stress fields with a finer lens. \Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e. through the line $x = 50\, b$. \Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$. Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses. In general, the non-singular formulation smoothes out the stress line plots. However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions. Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEperp.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syyEperp.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxyEperp.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syyEpar.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxyEpar.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xz}$.\label{sf:line_sxzscrew}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxzscrew.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yz}$.\label{sf:line_syzscrew}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syzscrew.pdf}}
    }
    \caption{Line plots of the image stresses at $x = 102.5641\, b$ (start of the third element) for the analytic image stresses, as well as those calculated with numeric and analytic tractions. The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$. (a) to (c) correspond to $\vec{b} = \vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b} = \vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b} = \vec{b}_{\textrm{s}}$.}
    \label{f:line_head_vs_ana_vs_num}
\end{figure}

We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $25.6410\, b$ (centre of the first element) to $1000\, b$ (centre of the 10th element). The line plots are taken from the second closest set of nodes in the positive $x$-direction i.e. at $x = 102.5641\, \sim 1076.9231\, b$.
\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
    }~
    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
    }~
    \subfloat[$\hat{\sigma}^\textrm{N}_{yy}$.\label{sf:sxxNepar2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:sxxepar11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar11.pdf}}
    }~
    \subfloat[$\hat{\sigma}^\textrm{A}_{xx}$.\label{sf:sxxAepar11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar11.pdf}}
    }~
    \subfloat[$\hat{\sigma}^\textrm{N}_{xx}$.\label{sf:sxxNepar11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar11.pdf}}
    }

    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot3.pdf}}
    }~
    \subfloat[$\sigma^\textrm{A}_{x}$.\label{sf:sxxAepartot2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot3.pdf}}
    }~
    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot2}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot3.pdf}}
    }

    \subfloat[$\sigma_{xx}$.\label{sf:sxxepartot11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEparTot11.pdf}}
    }~
    \subfloat[$\sigma^\textrm{A}_{xx}$.\label{sf:sxxAepartot11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEparTot11.pdf}}
    }~
    \subfloat[$\sigma^\textrm{N}_{xx}$.\label{sf:sxxNepartot11}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEparTot11.pdf}}
    }
    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. (a) to (c) and (g) to (i) at $(25.6410,\, 1000)\, b$; (d) to (f) and (j) to (l) at $(1000,\, 1000)\, b$. (a) to (g) image stresses; (g) to (l) total stresses.}
    \label{f:head_vs_ana_vs_num_epar2to11}
\end{figure}

\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar2}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar3.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_syyepar11}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar11.pdf}}
    }

    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot2}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot3.pdf}}
    }~
    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot11}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot11.pdf}}
    }

    \caption{Line plots corresponding to \cref{f:head_vs_ana_vs_num_epar2to11}. (a) and (c) are of image stresses; (b) and (d) are of total stresses. (a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 102.5641\, b$. (b) and (d) are of a dislocation at $(1000,\, 1000)\, b$ taken along the line $x \approx 1076.9231\, b$.}
    \label{f:line_head_vs_ana_vs_num_epar2to11}
\end{figure}
From the line plots, it can be observed that both analytic and numeric tractions converge to similar shapes to each other, which is to be expected. However it also becomes clear that the infinite-domain solution is not totally accurate for image stresses in finite domains due to edge effects. However, the glaring issue is that total stresses for each solution are significantly different as dislocations near the surface. The instability of Gauss quadrature when integrating rational functions tends to produce values that are outside the range of the infinite-domain solution, as well as being less smooth than the two other solutions.

@@

Figure \cref{f:simulation} shows the dramatic differences between simulations where the only difference was the method for traction calculation. The figures shown are not at equivalent times as the simulations using numeric tractions ran indefenitely, as the line tension equilibrated with the image forces on the traction-free surface. The simulation using analytic tractions ended when the dislocation completely exited the surface as expected.
\begin{figure}
    \subfloat[Analytic tractions $t = 0$.]
    {
        { \includegraphics[width=0.3\linewidth]{analytic_0.pdf}}
    }~
    \subfloat[Analytic tractions mid simulation.]
    {
        { \includegraphics[width=0.3\linewidth]{analytic_50.pdf}}
    }~
    \subfloat[Analytic tractions end.]
    {
        { \includegraphics[width=0.3\linewidth]{analytic_66.pdf}}
    }

    \subfloat[Numeric tractions $t = 0$.]
    {
        { \includegraphics[width=0.3\linewidth]{numeric_0.pdf}}
    }~
    \subfloat[Numeric tractions mid simulation.]
    {
        { \includegraphics[width=0.3\linewidth]{numeric_78.pdf}}
    }~
    \subfloat[Numeric tractions $t \to \infty$.]
    {
        { \includegraphics[width=0.3\linewidth]{numeric_156.pdf}}
    }
    \caption{Progression of simulations using both traction calculation methods.}
    \label{f:simulation}
\end{figure}

>>>>

It is also worth looking at the stress fields with a finer lens. \Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e. through the line $x = 50\, b$. \Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$. Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses. In general, the non-singular formulation smoothes out the stress line plots. However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions. Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syyEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxyEperp_leg.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syyEpar_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxyEpar_leg.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xz}$.\label{sf:line_sxzscrew}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxzscrew_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yz}$.\label{sf:line_syzscrew}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syzscrew_leg.pdf}}
    }
    \caption{Line plots of the image stresses at $x = 102.5641\, b$ (start of the third element) for the analytic image stresses, as well as those calculated with numeric and analytic tractions. The line corresponds to the first set of nodes away from the boundary at $x = 0\, b$. (a) to (c) correspond to $\vec{b} = \vec{b}_{\textrm{e1}}$, (d) to (f) $\vec{b} = \vec{b}_{\textrm{e2}}$ and (g) to (h) to $\vec{b} = \vec{b}_{\textrm{s}}$.}
    \label{f:line_head_vs_ana_vs_num}
\end{figure}

We also show examples of contour \cref{f:line_head_vs_ana_vs_num_epar2to11} and line plots \cref{f:line_head_vs_ana_vs_num_epar2to11} of the image and total stress fields as an edge dislocation with $\vec{b} = \vec{b}_{\textrm{e2}}$ moves from $25.6410\, b$ (centre of the first element) to $1000\, b$ (centre of the 10th element). The line plots are taken from the second closest set of nodes in the positive $x$-direction i.e. at $x = 102.5641\, \sim 1076.9231\, b$.
\begin{figure}
    \centering
    \subfloat[\hspace{-0.8cm}\label{sf:sxxepar2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEpar_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepar2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEpar_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepar2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEpar_leg.pdf}}
    }~
    \subfloat
    {
        {\includegraphics[height=0.227\linewidth]{images/sxxNAEpar_leg.pdf}}
    }

    \hspace*{0.28cm}\subfloat[\hspace{-0.8cm}\label{sf:sxxepar11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEpar11_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepar11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEpar11_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepar11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEpar11_leg.pdf}}
    }~
    {
    {\includegraphics[height=0.227\linewidth]{images/sxxNAEpar11_leg.pdf}}
    }

    \hspace*{0.28cm}\subfloat[\hspace{-0.8cm}\label{sf:sxxepartot2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEparTot3_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepartot2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEparTot3_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepartot2}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEparTot3_leg.pdf}}
    }~
    {
    {\includegraphics[height=0.227\linewidth]{images/sxxNAEparTot3_leg.pdf}}
    }

    \hspace*{0.28cm}\subfloat[\hspace{-0.8cm}\label{sf:sxxepartot11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEparTot11_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxAepartot11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEparTot11_leg.pdf}}
    }~
    \subfloat[\hspace{-0.8cm}\label{sf:sxxNepartot11}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEparTot11_leg.pdf}}
    }
    ~
    {
    {\includegraphics[height=0.227\linewidth]{images/sxxNAEparTot11_leg.pdf}}
    }
    \caption{Stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$. Subfigures (a) to (g) show image stresses; (h) to (m) show total stresses. In subfigures (a) to (c) and (h) to (j) the dislocation is found at $(25.6410,\, 1000)\, b$; (e) to (g) and (k) to (m) the dislocation is at $(1000,\, 1000)\, b$.}
    \label{f:head_vs_ana_vs_num_epar2to11}
\end{figure}

\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar2}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar3.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_syyepar11}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEpar11_leg.pdf}}
    }

    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot2}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot3_leg.pdf}}
    }~
    \subfloat[$\sigma_{xx}$.\label{sf:line_sxxeparTot11}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEparTot11_leg.pdf}}
    }

    \caption{Line plots corresponding to \cref{f:head_vs_ana_vs_num_epar2to11}. (a) and (c) are of the image stresses; (b) and (d) are of total stresses. (a) and (b) are of a dislocation at $(25.6410,\, 1000)\, b$, taken along the line $x = 102.5641\, b$. (b) and (d) are of a dislocation at $(1000,\, 1000)\, b$, taken along the line $x \approx 1076.9231\, b$.}
    \label{f:line_head_vs_ana_vs_num_epar2to11}
\end{figure}
From the line plots, it can be observed that both analytic and numeric tractions converge to similar shapes to each other, which is to be expected. However it also becomes clear that the infinite-domain solution is not totally accurate for image stresses in finite domains due to edge effects. However, the glaring issue is that total stresses for each solution are significantly different as dislocations near the surface. The instability of Gauss quadrature when integrating rational functions tends to produce values that are outside the range of the infinite-domain solution, as well as being less smooth than the two other solutions.

@@

Figure \cref{f:simulation} shows the dramatic differences between simulations where the only difference was the method for traction calculation. The figures shown are not at equivalent times as the simulations using numeric tractions ran indefenitely, as the line tension equilibrated with the image forces on the traction-free surface. The simulation using analytic tractions ended when the dislocation completely exited the surface as expected.
\begin{figure}
    \subfloat[Analytic tractions $t = 0$.]
    {
        {\includegraphics[width=0.3\linewidth]{analytic_0.pdf}}
    }~
    \subfloat[Analytic tractions mid simulation.]
    {
        {\includegraphics[width=0.3\linewidth]{analytic_50.pdf}}
    }~
    \subfloat[Analytic tractions end.]
    {
        {\includegraphics[width=0.3\linewidth]{analytic_66.pdf}}
    }

    \subfloat[Numeric tractions $t = 0$.]
    {
        {\includegraphics[width=0.3\linewidth]{numeric_0.pdf}}
    }~
    \subfloat[Numeric tractions mid simulation.]
    {
        {\includegraphics[width=0.3\linewidth]{numeric_78.pdf}}
    }~
    \subfloat[Numeric tractions $t \to \infty$.]
    {
        {\includegraphics[width=0.3\linewidth]{numeric_156.pdf}}
    }
    \caption{Progression of simulations using both traction calculation methods.}
    \label{f:simulation}
\end{figure}
